EasyMerge - A New Tool for Code Clones Refactoring

### 2014-03-07 paper/paper.tex
write more to paper

\title{EasyMerge - Clone Code Refactor}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Shengying Pan\\
       \affaddr{University of Waterloo}\\
       \email{s5pan@uwaterloo.ca}
% 2nd. author
\alignauthor
Haocheng Qin\\
       \affaddr{University of Waterloo}\\
       \email{h7qin@uwaterloo.ca}
% 3rd. author
\alignauthor Yahui Chen\\
       \affaddr{University of Waterloo}\\
       \email{y556chen@uwaterloo.ca}
\and  % use '\and' if you need 'another row' of author names
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

@@

\section{Clone Merging Algorithm}

>>>>

\title{EasyMerge - A New Tool for Code Clones Refactoring}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Shengying Pan\\
       \affaddr{School of Computer Science}\\
       \affaddr{University of Waterloo}\\
       \email{s5pan@uwaterloo.ca}
% 2nd. author
\alignauthor
Haocheng Qin\\
       \affaddr{School of Computer Science}\\
       \affaddr{University of Waterloo}\\
       \email{h7qin@uwaterloo.ca}
% 3rd. author
\alignauthor Yahui Chen\\
       \affaddr{School of Computer Science}\\
       \affaddr{University of Waterloo}\\
       \email{y556chen@uwaterloo.ca}
\and  % use '\and' if you need 'another row' of author names
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

More specifically, we pick CloneDigger \cite{bulychev}, an anti-unification duplicate code detection tool as our underlying clone detection approach. CloneDigger is one of the best available 
clone detection tools currently for its overall performance, coverage of multiple clone types, and availability. 
EasyMerge integrates CloneDigger as the pre-processing tool, analyze its output clone pairs, and recommend possible merges which can remove unnecessary clones without changing functionality of code base, creating reference conflicts, nor causing troubles to future code understanding and development.

The paper is structured as following: we first go through the basics, background, and current state of clone detection and code clone refactoring in general.
Then we introduce and discuss the fundamentals of CloneDigger and the anti-unification algorithm it is using to detect clones. Afterwards, we explain EasyMerge's
work flow and underlying techniques. And at the end, we set up testing environment and discuss the experimental results of running EasyMerge against several
open source projects of different scales.

@@

\section{EasyMerge}
